Generalized Bradley-Terry models

### 2025-02-20 inst/jss_hyper3_real.Rnw
include metadata

<<readsushi>>=
a <- as.matrix(read.table("sushi.txt"))
head(a)
@

@@

<<tryH,cache=TRUE>>=
wanted <- sample(seq_len(nrow(a)), 50, replace=TRUE, prob=a[,1])
H1888 <- make_sushi_H(a[wanted,-1], strength=1.888)
H1000 <- make_sushi_H(a[wanted,-1], strength=1.000)
@

>>>>

<<readsushi>>=
a <- as.matrix(read.table("sushi.txt",skip=22))
head(a)
@

@@

<<tryH,cache=TRUE>>=
wanted <- sample(seq_len(nrow(a)), 5, replace=TRUE, prob=a[,1])
H1888 <- make_sushi_H(a[wanted,-1], strength=1.888)
H1000 <- make_sushi_H(a[wanted,-1], strength=1.000)
@
